Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-07-31 paper/amia.tex
Auto Update from local Sharelatex

The current legal environment creates a difficult situation for scientists in the health care domain. Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}. Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}. More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system, a tool to generate an entire outpatient Electronic Health Record (EHR) based on population statistics \cite{walonoski_synthea_2018}. Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{prototype_architecture}
  \caption{System Architecture.}
  \label{fig:architecture}
\end{figure}
\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

@@

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Additionally, the other key constraint is having synthetic data be as close as possible to real data without reducing privacy.  While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger input dataset sizes.

>>>>

The current legal environment creates a difficult situation for scientists in the health care domain. Early examples of re-identification attacks \cite{sweeney_2002} have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}. Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}. More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system, a tool to generate an entire outpatient Electronic Health Record (EHR) based on population statistics \cite{walonoski_synthea_2018}. Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{prototype_architecture}
  \caption{System Architecture.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy. While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates very realistic synthetic data, but has a significant computational burden when generating synthetic data from larger input dataset sizes.
